A Theory of Bidirectional Type Synthesis for Simple Types

### 2023-07-12 tex/example.tex
[ tex ] Fix some typos and minor changes

\section{Examples}\label{sec:example}
Our theory works for any simply typed language that can be specified in a syntax-directed manner by a bidirectional binding signature, and is not confined to a specific language.
To showcase its general applicability, we present two additional examples:
\begin{enumerate}
\item \PCF with products and let bindings, and
\item spine calculus, a simply typed $\lambda$-calculus with applications in spine form.
\end{enumerate}
The first is a standard exercise in implementing a type synthesiser and the second is an example of a system with infinitely many operations.

\subsection{PCF with Products and Let Bindings}\label{subsec:PCF}
Although we have developed a theory for presenting a bidirectional type system and a condition for the decidability of bidirectional type synthesis, designing a bidirectional type system, or its signature, remains a creative activity.\footnote{This has also been the case for parsing: while there are grammar and parser generators, one still has to design a grammar to parse or disambiguate an ambiguous grammar.}
While the focus of this paper is not to design bidirectional type systems, we adopt the example of a bidirectional \PCF from \citet{Wadler2022}, which extends bidirectional simply typed $\lambda$-calculus in \Cref{sec:key-ideas} by adding the following rules:
\bgroup
\small
  \begin{mathpar}
    \inferrule{ }{\Gamma \vdash \mathtt{z} \chk \mathtt{nat}}
    \and
    \inferrule{\Gamma \vdash t \chk \mathtt{nat}}{\Gamma \vdash \mathtt{s}(t) \chk \mathtt{nat}}
    \and
    \inferrule{\Gamma \vdash t \syn \mathtt{nat} \and \Gamma \vdash t_0 \chk A \and \Gamma, x : \mathtt{nat} \vdash t_1 \chk A}{\Gamma \vdash \mathtt{ifz}(t_0; x.t_1)(t) \chk A}
    \and
    \inferrule{\Gamma \vdash t \chk A \and \Gamma \vdash u \chk B}{\Gamma \vdash (t, u) \chk A \times B}
    \and
    \inferrule{\Gamma \vdash t \syn A \times B}{\Gamma \vdash \mathtt{proj}_1(t) \syn A}
    \and
    \inferrule{\Gamma \vdash u \syn A \times B}{\Gamma \vdash \mathtt{proj}_2(u) \syn A}
    \\
    \inferrule{\Gamma, x : A \vdash t \chk A}{\Gamma \vdash \mu x.\, x \chk A}
    \and
    \inferrule{\Gamma \vdash t \syn A \and \Gamma, x : A \vdash u \chk B}{\Gamma \vdash \mathtt{let}\;x = t\;\mathtt{in}\;u\chk B}
  \end{mathpar}
\egroup

%In this language, there are additional type constructs other than $\bto$, so first we extend $\Sigma_{\bto}$ (\Cref{ex:type-signature-for-function-type}) with operations
In this language, we introduce additional type constructs apart from $\bto$.
To do so, we extend $\Sigma_{\bto}$ (as shown in \Cref{ex:type-signature-for-function-type}) with the operations $\mathsf{nat}$ and $\mathsf{times}$ such that
\[
  \arity({\mathsf{nat}}) = 0 \quad\text{and}\quad \arity({\mathsf{times}}) = 2
\]
enabling the introduction of $\mathtt{nat}$ and $A \times B$ as $\tyOp_{\mathsf{nat}}$ and $\tyOp_{\mathsf{times}}(A, B)$, respectively.
Following this, we also extend the bidirectional binding signature $\Omega_{\Lambda}^{\Leftrightarrow}$ with an operation for each rule above:
\begin{flalign*}
  &  \aritysymbol{\mathsf{z}}{\cdot}{\cdot}{\mathtt{nat}^{\chk}}
  && \aritysymbol{\mathsf{s}}{\cdot}{\mathtt{nat}^{\chk}}{\mathtt{nat}^{\chk}}
  && \aritysymbol{\mathsf{ifz}}{A}{\mathtt{nat}^{\syn}, A^{\chk}, A^{\chk}}{A^{\chk}} \\
  &  \aritysymbol{\mathsf{pair}}{A, B}{A^{\chk}, B^{\chk}}{A \times B^{\chk}}
  && \aritysymbol{\mathsf{proj}_1}{A, B}{A \times B^{\syn}}{A^{\syn}}
  && \aritysymbol{\mathsf{proj}_2}{A, B}{A \times B^{\syn}}{B^{\syn}} \\
  &  \aritysymbol{\mathsf{mu}}{A}{[A]A^{\chk}}{A^{\chk}}
  && \aritysymbol{\mathsf{let}}{A, B}{A^{\syn},[A]B^{\chk}}{B^{\chk}}
\end{flalign*}
With these operations, a straightforward check shows that every rule is mode-correct, therefore this as a mode-correct bidirectional type system.
As a result, we can instantiate the type synthesiser presented in \Cref{sec:type-synthesis} for this system, eliminating the need for re-implementation.

>>>>

\section{Examples}\label{sec:example}
Our theory works for any language that can be specified by a bidirectional binding signature.
To showcase its general applicability, we present two additional examples:
\begin{enumerate}
\item \PCF with products and let bindings, and
\item spine calculus, a simply typed $\lambda$-calculus with applications in spine form.
\end{enumerate}
The first is a standard exercise in implementing a type synthesiser and the second is an example of a system with infinitely many operations.

\subsection{PCF with Products and Let Bindings}\label{subsec:PCF}
Although we have developed a theory for presenting a bidirectional type system and a condition for the decidability of bidirectional type synthesis, designing a bidirectional type system, or its signature, remains a creative activity.\footnote{This has also been the case for parsing: while there are grammars and parser generators, one still has to design a grammar to parse or disambiguate an ambiguous grammar.}
While the focus of this paper is not to design bidirectional type systems, we adopt the example of a bidirectional \PCF from \citet{Wadler2022}, which extends bidirectional simply typed $\lambda$-calculus in \Cref{sec:key-ideas} by adding the following rules:
\bgroup
\small
  \begin{mathpar}
    \inferrule{ }{\Gamma \vdash \mathtt{z} \chk \mathtt{nat}}
    \and
    \inferrule{\Gamma \vdash t \chk \mathtt{nat}}{\Gamma \vdash \mathtt{s}(t) \chk \mathtt{nat}}
    \and
    \inferrule{\Gamma \vdash t \syn \mathtt{nat} \and \Gamma \vdash t_0 \chk A \and \Gamma, x : \mathtt{nat} \vdash t_1 \chk A}{\Gamma \vdash \mathtt{ifz}(t_0; x.t_1)(t) \chk A}
    \and
    \inferrule{\Gamma \vdash t \chk A \and \Gamma \vdash u \chk B}{\Gamma \vdash (t, u) \chk A \times B}
    \and
    \inferrule{\Gamma \vdash t \syn A \times B}{\Gamma \vdash \mathtt{proj}_1(t) \syn A}
    \and
    \inferrule{\Gamma \vdash u \syn A \times B}{\Gamma \vdash \mathtt{proj}_2(u) \syn A}
    \\
    \inferrule{\Gamma, x : A \vdash t \chk A}{\Gamma \vdash \mu x.\, x \chk A}
    \and
    \inferrule{\Gamma \vdash t \syn A \and \Gamma, x : A \vdash u \chk B}{\Gamma \vdash \mathtt{let}\;x = t\;\mathtt{in}\;u\chk B}
  \end{mathpar}
\egroup

%In this language, there are additional type constructs other than $\bto$, so first we extend $\Sigma_{\bto}$ (\Cref{ex:type-signature-for-function-type}) with operations
In this language, we introduce additional type constructs apart from $\bto$.
To do so, we extend $\Sigma_{\bto}$ (as shown in \Cref{ex:type-signature-for-function-type}) with the operations $\mathsf{nat}$ and $\mathsf{times}$ such that
\[
  \arity({\mathsf{nat}}) = 0 \quad\text{and}\quad \arity({\mathsf{times}}) = 2
\]
enabling the introduction of $\mathtt{nat}$ and $A \times B$ as $\tyOp_{\mathsf{nat}}$ and $\tyOp_{\mathsf{times}}(A, B)$, respectively.
Following this, we also extend the bidirectional binding signature $\Omega_{\Lambda}^{\Leftrightarrow}$ with an operation for each rule above:
\begin{flalign*}
  &  \aritysymbol{\mathsf{z}}{\cdot}{\cdot}{\mathtt{nat}^{\chk}}
  && \aritysymbol{\mathsf{s}}{\cdot}{\mathtt{nat}^{\chk}}{\mathtt{nat}^{\chk}}
  && \aritysymbol{\mathsf{ifz}}{A}{\mathtt{nat}^{\syn}, A^{\chk}, A^{\chk}}{A^{\chk}} \\
  &  \aritysymbol{\mathsf{pair}}{A, B}{A^{\chk}, B^{\chk}}{A \times B^{\chk}}
  && \aritysymbol{\mathsf{proj}_1}{A, B}{A \times B^{\syn}}{A^{\syn}}
  && \aritysymbol{\mathsf{proj}_2}{A, B}{A \times B^{\syn}}{B^{\syn}} \\
  &  \aritysymbol{\mathsf{mu}}{A}{[A]A^{\chk}}{A^{\chk}}
  && \aritysymbol{\mathsf{let}}{A, B}{A^{\syn},[A]B^{\chk}}{B^{\chk}}
\end{flalign*}
With these operations, a straightforward check shows that every rule is mode-correct, therefore this is a mode-correct bidirectional type system.
As a result, we can instantiate the type synthesiser presented in \Cref{sec:type-synthesis} for this system, eliminating the need for re-implementation.

### 2023-07-12 tex/sec1-intro.tex
[ tex ] Fix some typos and minor changes

The basic idea of bidirectional type synthesis is that while the problem of type inference is not decidable in general, for certain kinds of terms it is still possible to infer their types (for example, the type of a variable can be looked up in the context); for other kinds of terms, we can switch to the simpler problem of type checking, where the expected type of a raw term is also given so that there is more information to work with.
More formally, every judgement in a bidirectional type system is extended with a \emph{mode:}
\begin{enumerate*}
  \item $\Gamma |- \isTerm{t} \syn A$ for \emph{synthesis} and 
  \item $\Gamma |- \isTerm{t} \chk A$ for \emph{checking}.
\end{enumerate*}
The former indicates that the type~$A$ is computed as output, using both the context~$\Gamma$ and the term~$t$ as input, while for the latter, all three of $\Gamma$, $t$, and~$A$ are given as input.
The algorithm of a bidirectional type synthesiser can usually be `read off' from a well designed bidirectional type system: as the synthesiser traverses a raw term, it switches between synthesis and checking, following the modes assigned to the judgements in the typing rules.
%if a condition called \emph{mode-correctness} is satisfied.
%every synthesised type in a typing rule is determined by previously synthesised types from its premises and its input if checking.
As \citet{Pierce2000} noted, bidirectional type synthesis propagates type information locally within adjacent nodes of a raw term, and does not require unification as Damas--Milner type inference does.
Moreover, introducing long-distance unification constraints would even undermine the essence of locality in bidirectional type synthesis.

@@

Despite sharing the same basic idea, bidirectional typing has only been developed on a case-by-case basis without a theory; this situation is in stark contrast to parsing, which has a comprehensive theory together with widely applicable techniques and practical tools, notably parser generators.%
\footnote{The same could even be said for type checking in general, not just for bidirectional type systems.
While there are some efforts to generate type checkers grounded in unification~\citep{Gast2004,Grewe2015}, it should be noted that unification-based approaches are not suited to more complex type theories.
Moreover, their algorithms are not proved complete.}
%While it is straightforward to derive a type synthesis algorithm,
For bidirectional typing, \citet{Dunfield2021} could only present informal design principles that the community learned from individual systems, rather than a general theory providing logical specifications and rigorously proven properties for a class of systems.
Moreover, unlike the plethora of available parser generators, `type-synthesiser generators' rarely exist, so each type synthesiser has to be independently built from scratch.
To remedy the situation, we initiate a theory of bidirectional typing, which amounts to a verified type-synthesiser generator for syntax-directed bidirectional simple type systems.

@@

Our work is partly inspired by \varcitet{Wadler2022}{'s} textbook, where programming language concepts are formally introduced using the proof assistant~\Agda based on Martin-L\"of Type Theory, and one particular topic is bidirectional type synthesis for~\PCF.
Their treatment deviates from existing literature:
Traditionally, a type synthesis algorithm is presented as \emph{algorithmic system} relations such as $\Gamma |- \isTerm{t} \syn A \mapsto \isTerm{t}'$, denoting that annotations can be added to $\isTerm{t}$ in the surface language to produce $\isTerm{t}'$ of type $A$ in the core language.
Such an algorithm is then accompanied with \emph{soundness} and \emph{completeness} assertions such that the algorithm correctly synthesises the type of a raw term and every typable term can be synthesised if there are enough annotations.
By contrast, \citeauthor{Wadler2022} exploit the simultaneously computational and logical nature of Martin-L\"of type theory to formulate algorithmic soundness, completeness, and decidability in one go.
%(although they do not emphasise the difference of their approach from the traditional one)
Recall that the law of excluded middle $P + \neg P$ does not hold as an axiom for every $P$ in Martin-L\"of type theory and we say $P$ is \emph{decidable} if it holds for $P$.
For example, a proof of \emph{decidable equality}, i.e. $\forall x, y.~(x = y) + (x \neq y)$, decides whether they are equal and gives an identity proof explicitly if they are, which may or may not be possible depending on the domain of $x$~and~$y$.
Given that all proofs as programs terminate, logical decidability implies \emph{algorithmic decidability}.
Further, suppose a proof of the following statement:
\begin{quote}
  `For a context $\Gamma$ and a raw term $t$, either a typing derivation of\, $\Gamma |- t : A$ exists for some type~$A$ or any derivation of\, $\Gamma |- t : A$ for some type~$A$ leads to a contradiction'
\end{quote}
or rephrased succinctly as 
\begin{quote}
  `It is \underline{\emph{decidable}} for any $\Gamma$~and~$t$ whether $\Gamma |- t : A$ has a derivation for some~$A$'.
\end{quote}
It yields either a typing derivation for the given raw term~$t$ or a contradiction proof that such a derivation is impossible where the former case is algorithmic soundness and the latter algorithmic completeness in contrapositive form.
Then, both algorithmic soundness and completeness in original form are implied.
%echoing \citeauthor{Wadler2022}'s formulation as noted in \cref{re:type-synthesis-as-decidability-proof}.
%\todo{traditional completeness is still derivable from this `LEM'}
Our work takes the same approach but expands the scope significantly.
%That is, our decidable bidirectional type synthesis (\cref{thm:bidirectional-type-synthesis-checking}) provides algorithmic soundness, completeness, and decidability.

@@

The vision of formalising the metatheory of every programming language was initiated by the \PoplMark challenge~\citep{Aydemir2005}.
Earlier than \PoplMark, \citet{Altenkirch1993} commented that basic meta-operations and their meta-properties constitute the bulk of formalisation, motivating a number of frameworks~\citep{Ahrens2018,Fiore2022,Gheri2020,Ahrens2022,Allais2021} to define well-scoped/typed terms, substitution, term traversal, and their meta-properties universally.
One of the core gadgets of these frameworks is the notion of \emph{binding signatures} (coined by~\citet{Aczel1978} in line with the term \emph{signature} in universal algebra) for specifying type systems.
It is noteworthy that these state-of-the-art frameworks are basically restricted to simple types and cannot specify polymorphic types or dependent types yet, and only \citeauthor{Allais2021} discussed meta-operations beyond substitution.
Like these frameworks, our work is  built on a variant of binding signature for simple types.
Unlike these frameworks, we target constructions for a different part of programming language theory, namely the transition from a surface language (raw terms) to a core language (well-typed terms), and our type synthesiser is significantly more complex than those meta-operations previously considered.
Another difference is that several of the frameworks~\citep{Fiore2022,Allais2021,Ahrens2022} focus on intrinsically typed terms, whereas for our theory it is essential to use an extrinsic formulation to make it possible to relate a synthesised typing derivation with an input term.
This difference can be easily reconciled by converting extrinsic typing derivations to intrinsically typed terms though.

@@

In summary, we contribute a theory of bidirectional type synthesis that is
\begin{enumerate}
  \item \emph{simple yet general}, working for any syntax-directed bidirectional simple type system that can be specified by a bidirectional binding signature;
  \item \emph{constructive} based on Martin-L\"of type theory, and compactly formulated in a way that unifies computation and proof, preferring logical decidability over algorithmic soundness, completeness, and decidability; and mode decoration over annotatability.
\end{enumerate}
Our theory was first developed with \Agda and then translated to the mathematical vernacular.

This paper is structured as follows.
We first present a concrete overview of our theory using simply typed $\lambda$-calculus in \cref{sec:key-ideas}, prior to developing a general framework for specifying bidirectional type systems in \cref{sec:defs}.
Following this, we discuss mode decoration and related properties in \cref{sec:pre-synthesis}.
The most heavyweight technical contribution lies in \cref{sec:type-synthesis}, where we introduce mode-correctness and bidirectional type synthesis.
Some examples other than simply typed $\lambda$-calculus are given in \Cref{sec:example}.
We sketch the design of our formalisation in \cref{sec:formalisation} briefly.
We conclude in \cref{sec:future}, where we reflect on techniques that may improve the formal development and potential challenges in extending our theory to a more general setting.

>>>>

The basic idea of bidirectional type synthesis is that while the problem of type inference is not decidable in general, for certain kinds of terms it is still possible to infer their types (for example, the type of a variable can be looked up in the context); for other kinds of terms, we can switch to the simpler problem of type checking, where the expected type of a term is also given so that there is more information to work with.
More formally, every judgement in a bidirectional type system is extended with a \emph{mode:}
\begin{enumerate*}
  \item $\Gamma |- \isTerm{t} \syn A$ for \emph{synthesis} and 
  \item $\Gamma |- \isTerm{t} \chk A$ for \emph{checking}.
\end{enumerate*}
The former indicates that the type~$A$ is computed as output, using both the context~$\Gamma$ and the term~$t$ as input, while for the latter, all three of $\Gamma$, $t$, and~$A$ are given as input.
The algorithm of a bidirectional type synthesiser can usually be `read off' from a well-designed bidirectional type system: as the synthesiser traverses a raw term, it switches between synthesis and checking, following the modes assigned to the judgements in the typing rules.
%if a condition called \emph{mode-correctness} is satisfied.
%every synthesised type in a typing rule is determined by previously synthesised types from its premises and its input if checking.
As \citet{Pierce2000} noted, bidirectional type synthesis propagates type information locally within adjacent nodes of a term, and does not require unification as Damas--Milner type inference does.
Moreover, introducing long-distance unification constraints would even undermine the essence of locality in bidirectional type synthesis.

@@

Despite sharing the same basic idea, bidirectional typing has only been developed on a case-by-case basis without a theory; this situation is in stark contrast to parsing, which has general theories together with widely applicable techniques and practical tools, notably parser generators.%
\footnote{The same could even be said for type checking in general, not just for bidirectional type systems.
While there are some efforts to generate type checkers grounded in unification~\citep{Gast2004,Grewe2015}, it should be noted that unification-based approaches are not suited to more complex type theories.
Moreover, their algorithms are not proved complete.}
%While it is straightforward to derive a type synthesis algorithm,
For bidirectional typing, \citet{Dunfield2021} could only present informal design principles that the community learned from individual systems, rather than a general theory providing logical specifications and rigorously proven properties for a class of systems.
Moreover, unlike the plethora of available parser generators, `type-synthesiser generators' rarely exist, so each type synthesiser has to be independently built from scratch.
To remedy the situation, we initiate a theory of bidirectional typing, which amounts to a verified type-synthesiser generator for syntax-directed simple type systems.

@@

Our work is partly inspired by \varcitet{Wadler2022}{'s} textbook, where programming language concepts are formally introduced using the proof assistant~\Agda based on Martin-L\"of Type Theory, and one particular topic is bidirectional type synthesis for~\PCF.
Their treatment deviates from existing literature:
Traditionally, a type synthesis algorithm is presented as \emph{algorithmic system} relations such as $\Gamma |- \isTerm{t} \syn A \mapsto \isTerm{t}'$, denoting that annotations can be added to $\isTerm{t}$ in the surface language to produce $\isTerm{t}'$ of type $A$ in the core language.
Such an algorithm is then accompanied with \emph{soundness} and \emph{completeness} assertions such that the algorithm correctly synthesises the type of a raw term and every typable term can be synthesised if there are enough annotations.
By contrast, \citeauthor{Wadler2022} exploit the simultaneously computational and logical nature of Martin-L\"of type theory to formulate algorithmic soundness, completeness, and decidability in one go.
%(although they do not emphasise the difference of their approach from the traditional one)
Recall that the law of excluded middle $P + \neg P$ does not hold as an axiom for every $P$ in Martin-L\"of type theory, and we say $P$~is \emph{decidable} if the law holds for~$P$.
For example, a proof of \emph{decidable equality}, i.e. $\forall x, y.~(x = y) + (x \neq y)$, decides whether $x$~and~$y$ are equal and accordingly gives an identity proof or a refutation explicitly; such a decidability proof may or may not be possible depending on the domain of $x$~and~$y$, and is non-trivial.
Given that all proofs as programs terminate, logical decidability implies \emph{algorithmic decidability}.
Further, suppose a proof of the following statement:
\begin{quote}
  `For a context $\Gamma$ and a raw term $t$, either a typing derivation of\, $\Gamma |- t : A$ exists for some type~$A$ or any derivation of\, $\Gamma |- t : A$ for some type~$A$ leads to a contradiction'
\end{quote}
or rephrased succinctly as 
\begin{quote}
  `It is \underline{\emph{decidable}} for any $\Gamma$~and~$t$ whether $\Gamma |- t : A$ has a derivation for some~$A$'.
\end{quote}
It yields either a typing derivation for the given raw term~$t$ or a contradiction proof that such a derivation is impossible where the former case is algorithmic soundness and the latter algorithmic completeness in contrapositive form.
Then, both algorithmic soundness and completeness in original form are implied.
%echoing \citeauthor{Wadler2022}'s formulation as noted in \cref{re:type-synthesis-as-decidability-proof}.
%\todo{traditional completeness is still derivable from this `LEM'}
Our work takes the same approach but expands the scope significantly.
%That is, our decidable bidirectional type synthesis (\cref{thm:bidirectional-type-synthesis-checking}) provides algorithmic soundness, completeness, and decidability.

@@

The vision of formalising the metatheory of every programming language was initiated by the \PoplMark challenge~\citep{Aydemir2005}.
Earlier than \PoplMark, \citet{Altenkirch1993} commented that basic meta-operations and their meta-properties constitute the bulk of formalisation, motivating a number of frameworks~\citep{Ahrens2018,Fiore2022,Gheri2020,Ahrens2022,Allais2021} to define well-scoped/typed terms, substitution, term traversal, and their meta-properties universally (in the sense of universal algebra).
One of the core gadgets of these frameworks is the notion of \emph{binding signatures} (coined by~\citet{Aczel1978} in line with the term \emph{signature} in universal algebra) for specifying type systems.
It is noteworthy that these state-of-the-art frameworks are basically restricted to simple types and cannot specify polymorphic types or dependent types yet, and only \citeauthor{Allais2021} discussed meta-operations beyond substitution.
Like these frameworks, our work is  built on a variant of binding signature for simple types.
Unlike these frameworks, we target constructions for a different part of programming language theory, namely the transition from a surface language (raw terms) to a core language (well-typed terms), and our type synthesiser is significantly more complex than those meta-operations previously considered.
Another difference is that several of the frameworks~\citep{Fiore2022,Allais2021,Ahrens2022} focus on intrinsically typed terms, whereas for our theory it is essential to use an extrinsic formulation to make it possible to relate a synthesised typing derivation with an input term.
This difference can be easily reconciled by converting extrinsic typing derivations to intrinsically typed terms though.

@@

In summary, we contribute a theory of bidirectional type synthesis that is
\begin{enumerate}
  \item \emph{simple yet general}, working for any syntax-directed bidirectional simple type system that can be specified by a bidirectional binding signature;
  \item \emph{constructive} based on Martin-L\"of type theory, and compactly formulated in a way that unifies computation and proof, preferring logical decidability over algorithmic soundness, completeness, and decidability; and mode decoration over annotatability.
\end{enumerate}
Our theory was first developed in \Agda and then translated to the mathematical vernacular.

This paper is structured as follows.
We first present a concrete overview of our theory using simply typed $\lambda$-calculus in \cref{sec:key-ideas}, prior to developing a general framework for specifying bidirectional type systems in \cref{sec:defs}.
Following this, we discuss mode decoration and related properties in \cref{sec:pre-synthesis}.
The most heavyweight technical contribution lies in \cref{sec:type-synthesis}, where we introduce mode-correctness and bidirectional type synthesis.
Some examples other than simply typed $\lambda$-calculus are given in \Cref{sec:example}.
We briefly sketch the design of our formalisation in \cref{sec:formalisation} and conclude in \cref{sec:future} with potential challenges in extending our theory to a more general setting.
